---
title: "A Bayesian VAR Suite for Forecasting the Australian Economy"
subtitle: "What it forecasts, how it is judged, and what the evidence says — 1 to 12 quarters ahead"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
    fig-align: center
execute:
  echo: false
  warning: false
---

```{r setup}
suppressPackageStartupMessages({library(knitr)})
tabdir <- "../output/tables"; figdir <- "../output/figures"
rd <- function(f) if (file.exists(file.path(tabdir, f)))
  read.csv(file.path(tabdir, f), stringsAsFactors = FALSE) else NULL
spec    <- rd("transform_spec.csv")
scores  <- rd("scores_by_horizon.csv")
scores_ex <- rd("scores_by_horizon_excovid.csv")
diag    <- rd("diagnostics.csv")
wfinal  <- rd("final_weights.csv")
dm      <- rd("dm_tests.csv")
pitt    <- rd("pit_tests.csv")
ep      <- rd("event_probabilities.csv")
fc      <- read.csv("../output/forecasts/forecast_table.csv")
cfc     <- if (file.exists("../output/forecasts/forecast_table_conditional.csv"))
  read.csv("../output/forecasts/forecast_table_conditional.csv") else NULL

# LEVEL-error view (the headline): cumulative level (cum, + q at h=1) for
# growth-modelled targets; the rate level (q) for level-modelled targets.
.dlog_tgt <- spec$variable[spec$transform == "dlog" & spec$target %in% c(TRUE, "TRUE")]
.lev_meas <- function(v) if (v %in% .dlog_tgt) "cum" else "q"
.tgt <- spec$variable[spec$target %in% c(TRUE, "TRUE")]
.lvl_view <- function(sc) do.call(rbind, lapply(.tgt, function(v) {
  if (v %in% .dlog_tgt)
    rbind(sc[sc$variable == v & sc$measure == "cum", ],
          sc[sc$variable == v & sc$measure == "q" & sc$h == 1, ])
  else sc[sc$variable == v & sc$measure == "q", ]
}))
lvl <- .lvl_view(scores)
dm_lvl <- if (!is.null(dm)) do.call(rbind, lapply(.tgt, function(v)
  dm[dm$variable == v & dm$measure == .lev_meas(v), ])) else NULL
cfgy <- yaml::read_yaml("../config/config.yml")$default
src <- cfgy$data$source
n_origins <- cfgy$evaluation$max_origins
lbl <- setNames(spec$label, spec$variable)
src_note <- if (identical(src, "synthetic")) {
  "**This run used simulated (synthetic) data**, which exists so the pipeline can run offline; the results validate the machinery, not Australian dynamics. Re-run with `data.source: real` for substantive results."
} else {
  "Results are based on final-vintage published data; real-time vintages are not used, so revision-sensitive comparisons (especially GDP at short horizons) should be read with care — see the limitations section."
}
# computed exec-summary ingredients: best individual model per target (level
# CRPS, mean over horizons), and the equal pool's rank
best_by_target <- do.call(rbind, lapply(.tgt, function(v) {
  d <- lvl[lvl$variable == v, ]
  agg <- aggregate(crps ~ member, d, mean)
  agg <- agg[order(agg$crps), ]
  data.frame(variable = v, best = agg$member[1],
             best_single = agg$member[!grepl("^combo_", agg$member)][1],
             equal_rank = match("combo_equal", agg$member), n = nrow(agg))
}))
```

::: {.callout-note title="If you read nothing else"}
This project forecasts **GDP growth, trimmed-mean inflation, the unemployment
rate and the cash rate** for Australia, 1–12 quarters ahead, using
`r length(cfgy$suite)` Bayesian VAR models plus `r length(cfgy$benchmarks)`
simple statistical benchmarks, all **combined into one pooled probability
forecast**. Every model was tested by re-living the past: at each of
`r n_origins` historical quarters it was re-estimated using only the data
available at that date, made to forecast, and scored against what actually
happened. The headline outputs are (i) the current fan-chart forecasts and
event probabilities (§6), and (ii) the evidence on which models are reliable
at which horizon (§5). `r src_note`
:::

## 1. What this is, in plain terms

**The task.** Central-bank forecasting is not one prediction — it is a
*distribution* over what might happen, at every horizon from next quarter to
three years out. This pipeline produces those distributions ("density
forecasts") for the four policy variables, together with honest evidence
about how good they are.

**Why a suite rather than one model.** No single model is best everywhere:
tightly-disciplined models are robust three years out but sluggish next
quarter; richly-parameterised models excel near-term and wander far-term;
simple benchmarks are surprisingly hard to beat for inflation. So the
production forecast is a **weighted pool** of all models' distributions, and
most of this report is about *which models earn their place and where*.

::: {.callout-tip title="Where the equations live"}
This report explains *what the suite does and what it finds*, in words. For
the full mathematical specification — every prior, posterior, Gibbs step,
forecasting recursion, scoring rule and combination formula, with equations
and config keys — see the companion **technical reference**
(`methodology.html`).
:::

**Why "small open economy" is in the title.** Australia does not move world
demand, world commodity prices, or the federal funds rate. Every VAR here
partitions its variables into a **foreign block** (world activity, commodity
prices, the US policy rate) and a **domestic block**, and imposes **block
exogeneity**: foreign variables evolve as if Australia did not exist, while
domestic variables respond to the world. Without this, a model happily
"learns" from 30 years of data that Australian GDP drives world commodity
prices — a spurious channel that quietly corrupts medium-term forecasts. One
suite member (`small_unres`) deliberately *omits* the restriction so we can
measure what it buys (§5.4).

**The data.** `r nrow(spec)` quarterly series
(`r sum(spec$block == "foreign")` foreign, `r sum(spec$block == "domestic")`
domestic), Australian data from the RBA and ABS, the foreign block from FRED.
Data source for this run: **`r src`**.

## 2. How to read the numbers (a two-minute guide)

Every model produces, for each variable and horizon, a full probability
distribution. Three scores are used throughout, each answering a different
question:

| Score | Question it answers | Better is |
|---|---|---|
| **RMSE** | Was the *centre* of the forecast right? (root-mean-squared error of the point forecast) | lower |
| **CRPS** | Was the *whole distribution* right? Roughly: the average distance between the forecast distribution and the outcome. It rewards being close *and* being honest about uncertainty. | lower |
| **Log score** | How much probability did the model assign to what actually happened? It punishes overconfidence brutally: call an outcome "nearly impossible" and watch it occur, and your average never recovers. | higher |

CRPS and the log score usually agree. They diverge in episodes like 2020,
when realizations landed far in the tails — the log score is dominated by
those few quarters, CRPS much less so. That is why both are reported, and
why score tables come in a with-COVID and an ex-COVID variant.

**Calibration and PITs.** A forecast distribution is *calibrated* if events
it calls "20% likely" happen about 20% of the time. The tool for checking
this is the **PIT** (probability integral transform): where in the forecast
distribution did the outcome land, on a 0–1 scale? For a calibrated
forecaster these values are uniform — the histogram is flat. A **hump** in
the middle means intervals were too wide (overly cautious); a **U-shape**
means too narrow (overconfident); a lopsided histogram means biased.

**Two views of accuracy.** Growth variables can be scored on each quarter's
outcome in isolation, or on where the accumulated *level* ends up. The
headline here is the **level** view: "where is the price level / real GDP /
the unemployment rate in two years?" — which is what policy cares about, and
which exposes models whose small quarterly biases compound. A concrete
example: a model that forecasts GDP growth of 0.7% every quarter when the
truth averages 0.6% looks fine quarter by quarter (error 0.1pp) but is 1.2%
too high on the GDP level after three years. The quarterly view is also
reported (the scorecard's §3) because it answers the complementary question
— "did the model get the near-term dynamics right?"

**Horizons.** h = 1 is one quarter ahead; h = 12 is three years. Combination
weights are estimated per horizon **bucket** — near (1–4), medium (5–8), far
(9–12) — because the best model changes with horizon.

**Members vs combinations.** Rows named `combo_*` are pools (weighted
mixtures of all members' densities), not models. `combo_equal` weights all
members equally; it is the famously hard-to-beat benchmark ("the forecast
combination puzzle"). The performance-weighted schemes (`logscore`, `crps`,
`pool`) adapt weights to the recent track record — trained on the same level
loss the headline reports, with the COVID window excluded so a few extreme
quarters cannot dictate the weights (README D20). `combo_bma` is a
diagnostic, not a forecast: it shows which single model the data likes best.

## 3. The models

```{r}
kable(spec[, c("variable", "label", "block", "transform", "delta", "ss_mean", "ss_sd")],
      digits = 2,
      caption = "The variables. transform: how each series enters the models (dlog = quarterly log-change, i.e. growth; level = as is). delta: the prior's default persistence (1 = behaves like a random walk, 0 = mean-reverting). ss_mean/ss_sd: the steady-state member's prior on the long-run value (e.g. inflation anchored at 2.5% p.a. — the target midpoint).")
```

Eight VARs and four univariate benchmarks. What distinguishes the VARs, in
one line each (full profiles with their evaluation evidence:
`model_scorecard.md` §6):

- **`small_minn`** — the workhorse: 8 variables, data-driven shrinkage,
  long-run priors on the persistent series.
- **`small_ss`** — the *steady-state* member: its long-run means are anchored
  to economics (inflation 2.5%, NAIRU 4.5%, neutral cash rate 3.5%) instead of
  sample averages; matters most at h ≥ 8, where every VAR forecast converges
  to its long-run mean.
- **`small_sv`** — *stochastic volatility*: the size of shocks changes over
  time, so uncertainty bands widen and narrow with the environment; fat-tailed
  errors absorb outliers.
- **`small_loose_p5` / `small_tight`** — deliberately under- and over-shrunk
  variants: the data speak more / less. They bracket the workhorse.
- **`medium_minn` / `medium_conj`** — 13-variable systems (adding wages,
  employment, consumption, terms of trade, the 10-year yield), with SV and
  constant volatility respectively.
- **`small_unres`** — the **control**: identical to the workhorse but
  *without* block exogeneity. Its only job is to measure whether the
  restriction helps (§5.4).

Benchmarks: a random walk (`rw`), a Bayesian AR(4) (`ar4`), the
Stock–Watson-style trend-plus-noise model with stochastic volatility
(`ucsv`, the canonical inflation benchmark), and the unconditional mean
(`ucmean`). They are cheap, genuinely different, and every VAR must beat
them to justify its complexity.

**The COVID quarters.** Three quarters of 2020 are 5–30σ events; untreated,
they wreck coefficient and volatility estimates. Constant-volatility members
down-weight those quarters' *likelihood contribution* with scale factors
estimated recursively (Lenza–Primiceri); SV members absorb them through
fat-tailed errors instead. Nothing is deleted: the observations still enter
the forecast jump-off. See README D17 for the full design and its empirical
validation.

## 4. How the evaluation works

The evaluation re-lives history. At each forecast origin *t* (there are
`r n_origins`, ending one quarter before the sample ends), every member is
re-estimated **using only data through t** — including the data-driven
tightness selection and the COVID scale estimation, which are re-run inside
each origin — and forecasts 1–12 quarters ahead. Forecasts are scored against
what happened. Combination weights at *t* use only forecast scores whose
outcome had been realized by *t*.

"No look-ahead" is a correctness property here, not a slogan: an automated
test corrupts all post-origin data (×10⁶) and requires every forecast draw to
be bit-identical; a reproducibility test requires identical results from
identical seeds; and block exogeneity is verified numerically on every fit.
All are enforced as hard gates — the pipeline refuses to produce output if
one fails (§7).

## 5. Results

### 5.1 The headline: level accuracy by horizon

*How to read the figures: one panel per target; the y-axis is mean CRPS of
the level forecast (lower = better); each line is a model (dashed = pooled
combinations). Level errors accumulate the whole path, so curves rise with
horizon mechanically — compare models at a horizon, not horizons with each
other.*

```{r, results="asis"}
for (v in unique(fc$variable)) {
  f <- file.path(figdir, sprintf("crps_by_h_%s.png", v))
  if (file.exists(f)) cat(sprintf("![](%s){width=85%%}\n\n", f))
}
```

```{r}
tab <- lvl[lvl$h %in% c(1, 4, 8, 12), ]
tab <- reshape(tab[, c("member","variable","h","crps")],
               idvar = c("member","variable"), timevar = "h", direction = "wide")
kable(tab[order(tab$variable, tab$crps.1), ], digits = 3, row.names = FALSE,
      caption = "Mean level CRPS at h = 1, 4, 8, 12 (lower = better). For GDP and inflation this scores the cumulative level from the forecast origin; for unemployment and the cash rate, the rate itself.")
```

**Takeaways (computed from the table above):**

```{r, results="asis"}
for (i in seq_len(nrow(best_by_target))) {
  b <- best_by_target[i, ]
  cat(sprintf("- **%s**: best forecaster overall is `%s`; the best individual model is `%s`; the equal-weight pool ranks %d of %d.\n",
              lbl[[b$variable]], b$best, b$best_single, b$equal_rank, b$n))
}
```

```{r}
lsx <- lvl[lvl$h %in% c(1, 4, 8, 12), ]
lsx <- reshape(lsx[, c("member","variable","h","logdens")],
               idvar = c("member","variable"), timevar = "h", direction = "wide")
kable(lsx[order(lsx$variable, -lsx$logdens.1), ], digits = 2, row.names = FALSE,
      caption = "Mean level log predictive density (higher = better). −Inf marks a model that assigned essentially zero probability to an outcome that occurred; pooled combinations never do — one argument for pooling.")
```

### 5.2 The COVID caveat, quantified

Mean scores over a window containing 2020 are dominated by a few quarters.
The same tables excluding realizations in 2020Q1–2021Q2 are in
`output/tables/scores_by_horizon_excovid.csv`; where a ranking reverses
between the two, the ex-COVID one is usually the better guide to normal
times.

```{r}
if (!is.null(scores_ex)) {
  lvx <- .lvl_view(scores_ex)
  cmp <- merge(aggregate(crps ~ member, lvl[lvl$h <= 4, ], mean),
               aggregate(crps ~ member, lvx[lvx$h <= 4, ], mean),
               by = "member", suffixes = c("_all", "_excovid"))
  cmp <- cmp[order(cmp$crps_excovid), ]
  kable(cmp, digits = 3, row.names = FALSE,
        caption = "Near-horizon (h 1-4) mean level CRPS, all origins vs excluding COVID realizations: how much of each model's score is one episode.")
}
```

### 5.3 Do the combinations earn their keep?

Equal weights are the benchmark to beat, and the honest summary is that
pooled forecasts buy **insurance and calibration** more than raw accuracy: a
pool never takes a −∞ log score, never rides one model's failure mode, and
its intervals are better calibrated — but at any single variable × horizon a
well-chosen member usually noses ahead. Weight-training details (level loss,
COVID window excluded, shrinkage toward equal) are in README D20 — the
2026-07 audit showed that *without* those guards, log-score weights handed
the far-horizon GDP bucket to the random walk on the strength of three 2020
quarters.

Final-origin weights of the optimal pool (averaged over targets):

```{r}
wp <- aggregate(weight ~ member + bucket, data = wfinal[wfinal$scheme == "pool", ],
                FUN = mean)
wp <- reshape(wp, idvar = "member", timevar = "bucket", direction = "wide")
names(wp) <- sub("^weight\\.", "", names(wp))
kable(wp[order(-wp$near), ], digits = 3, row.names = FALSE,
      caption = "Optimal-pool weights by horizon bucket (final origin, averaged over targets). Equal weight would be 1/12 ≈ 0.083 per member.")
```

```{r}
bma <- aggregate(weight ~ member, data = wfinal[wfinal$scheme == "bma", ], FUN = mean)
kable(bma[order(-bma$weight), ], digits = 3, row.names = FALSE,
      caption = "BMA diagnostic (no shrinkage): which single model the data favour. By construction it concentrates; it is reported to be read, not used.")
```

```{r, results="asis"}
fs <- list.files(figdir, pattern = "^weights_pool_.*near", full.names = TRUE)
if (length(fs)) {
  cat("*Weight evolution over time (near bucket): a member earning weight is a member that has been forecasting well lately.*\n\n")
  for (f in fs) cat(sprintf("![](%s){width=85%%}\n\n", f))
}
```

### 5.4 What does block exogeneity buy? (the control experiment)

`small_unres` is `small_minn` without the small-open-economy restriction.
If the restriction helps, `small_minn` should win — especially at medium/far
horizons where spurious domestic→foreign feedback compounds.

```{r}
d <- lvl[lvl$member %in% c("small_minn", "small_unres"), ]
if (length(unique(d$member)) == 2) {
  cmp <- aggregate(crps ~ member + variable, d[d$h %in% 5:12, ], mean)
  cmp <- reshape(cmp, idvar = "variable", timevar = "member", direction = "wide")
  names(cmp) <- sub("^crps\\.", "", names(cmp))
  cmp$restriction_helps <- ifelse(cmp$small_minn < cmp$small_unres, "yes", "no")
  kable(cmp, digits = 3, row.names = FALSE,
        caption = "Mean level CRPS, h = 5-12: the block-exogenous workhorse vs its unrestricted twin. 'yes' = imposing the SOE structure improved the forecast.")
} else {
  cat("*small_unres not present in this run's scores.*")
}
```

### 5.5 Statistical significance

Diebold–Mariano tests ask whether a score difference is larger than its
sampling noise (Harvey-corrected, autocorrelation-robust). Stars: `***` 1%,
`**` 5%, `*` 10%. These losses are high-variance — dominated by a few
episodes — so **absence of stars is weak evidence of nothing**; the tests
have low power at long horizons.

```{r}
if (!is.null(dm_lvl) && nrow(dm_lvl)) {
  d1 <- dm_lvl[dm_lvl$h %in% c(4, 8, 12) & grepl("^combo_", dm_lvl$member), ]
  kable(d1[order(d1$variable, d1$h), c("member","reference","variable","h",
        "dm_crps","p_crps","sig_crps")], digits = 3, row.names = FALSE,
        caption = "Level-CRPS DM tests: pooled combinations vs the AR(4) and random-walk benchmarks. Negative statistic = the combination is more accurate.")
}
```

## 6. The current forecasts

Fan charts from the optimal-pool combination at the final origin. *How to
read a fan chart: the line is history; the dashed line is the median
forecast; the bands cover 30%/50%/70%/90% of the predictive distribution —
the point is the width as much as the centre.*

```{r, results="asis"}
fs <- list.files(figdir, pattern = "^fan_pool_", full.names = TRUE)
for (f in fs) cat(sprintf("![](%s){width=85%%}\n\n", f))
```

```{r}
cb <- fc[fc$member == "combo_pool", ]
kable(cb[cb$h %in% c(1, 2, 4, 8, 12), c("variable","h","point","lo90","hi90")],
      digits = 2, row.names = FALSE,
      caption = "Combined (optimal pool) forecasts: median and 90% interval. Units: quarterly % growth for GDP and inflation; % for unemployment and the cash rate.")
```

### 6.1 Event probabilities

Point forecasts hide the questions policy actually asks. From the pooled
predictive distribution (probability-level pooling, which is exact for a
linear pool):

```{r, results="asis"}
f <- file.path(figdir, "event_probabilities.png")
if (file.exists(f)) cat(sprintf("![](%s){width=95%%}\n\n", f))
```

```{r}
if (!is.null(ep)) {
  eps <- ep[ep$h %in% c(2, 4, 8, 12), c("event", "h", "prob")]
  eps <- reshape(eps, idvar = "event", timevar = "h", direction = "wide")
  names(eps) <- sub("^prob\\.", "h=", names(eps))
  kable(eps, digits = 2, row.names = FALSE,
        caption = "Event probabilities by horizon from the final pooled forecast (thresholds configurable in report.events).")
}
```

### 6.2 Scenario: forecasts under imposed profiles

A forecast round rarely lets every variable float. The standard pattern:
the **global block is taken as given over the whole projection window**
(the international forecasts are an input, not an output), while domestic
variables with good nowcasts — quarterly CPI, the unemployment rate — are
pinned for **one quarter only**. The suite accepts exactly this ragged
pattern: profiles per variable, each over its own horizon, supplied as a
CSV (`report.conditional.profiles_file`) or inline in the config, and
imposed by Waggoner–Zha conditional simulation — the joint shock
distribution is updated exactly, so un-pinned variables (GDP, the cash
rate) respond to the profiles through both the lag dynamics and the
contemporaneous shock correlations, and the un-pinned quarters of a
partially-pinned variable revert to model-driven forecasts consistent with
the pinned quarter. See README D23 for the file format and mechanics;
`data/example_forecast_profiles.csv` is the worked example.

```{r, results="asis"}
if (!is.null(cfc)) {
  cat(sprintf("This run imposes profiles for **%s** (illustrative example values — replace the profiles file each round). In the table, `imposed = TRUE` marks quarters that were pinned rather than forecast; intervals there collapse to the imposed value by construction.\n\n",
              gsub("\\+", ", ", unique(cfc$conditioned_on)[1])))
  show <- cfc[cfc$h %in% c(1, 2, 4, 8, 12),
              c("variable","h","target_date","point","lo90","hi90","imposed")]
  kable(show, digits = 2, row.names = FALSE,
        caption = "Scenario forecasts (VAR members, equal-weight pool) under the imposed profiles, alongside the unconditional forecasts in the table above.")
} else {
  cat("*No profiles configured for this run. Set `report.conditional.profiles_file` in `config/config.yml` (see `data/example_forecast_profiles.csv` and README D23).*\n")
}
```

## 7. Is any of this trustworthy? (calibration and diagnostics)

### 7.1 Calibration

PIT histograms (see §2 for how to read them), h = 1 and h = 4:

```{r, results="asis"}
for (f in c("pit_h1.png", "pit_h4.png")) {
  p <- file.path(figdir, f)
  if (file.exists(p)) cat(sprintf("![](%s){width=95%%}\n\n", p))
}
```

At horizons beyond 1 the usual uniformity test is invalid (overlapping
forecasts make PITs serially correlated), so the table below tests the first
two moments with autocorrelation-robust standard errors: **location** (is the
mean PIT 0.5? — bias) and **dispersion** (is the PIT variance 1/12? — too
wide/too narrow), per horizon. Small p-values flag a problem.

```{r}
if (!is.null(pitt)) {
  bad <- pitt[(!is.na(pitt$p_location) & pitt$p_location < 0.05) |
              (!is.na(pitt$p_dispersion) & pitt$p_dispersion < 0.05), ]
  bad <- bad[order(bad$member, bad$variable, bad$h), ]
  if (nrow(bad)) {
    kable(head(bad, 30), digits = 3, row.names = FALSE,
          caption = "PIT moment-test failures at the 5% level (full table: output/tables/pit_tests.csv). mean_pit > 0.5 = forecasts too low on average; var_pit > 1/12 ≈ 0.083 = intervals too narrow.")
  } else {
    cat("No member fails the PIT moment tests at the 5% level.")
  }
}
```

### 7.2 Hard gates

These are enforced — the pipeline stops if one fails:

```{r}
kable(diag, digits = 4,
      caption = "Per-member diagnostics. block_exog_max: largest posterior-mean domestic coefficient in a foreign equation (should be ~0; small_unres is exempt by design — it is the control). ess_min: worst-case MCMC effective sample size. sanity: forecasts finite, non-explosive, converging to sensible long-run values.")
```

- **Block exogeneity binds** (max violation
  `r format(if ("block_exog_exempt" %in% names(diag)) max(diag$block_exog_max[!diag$block_exog_exempt]) else max(diag$block_exog_max), digits = 2)`
  across all restricted members and origins).
- **No look-ahead:** corrupting all post-origin data leaves every forecast
  draw bit-identical.
- **Reproducibility:** same seed ⇒ identical results, regardless of parallel
  scheduling.

## 8. Honest limitations and the roadmap

- **Final-vintage data.** Every origin sees today's published history, not
  what a forecaster saw at the time. Australian GDP and employment revisions
  are material, so short-horizon GDP rankings especially should be read as
  indicative. *Scoped extension:* a vintage database for GDP alone would
  upgrade the h = 1–2 claims; no reliable key-free machine-readable vintage
  source currently exists for the full panel.
- **The world is proxied by the US.** World activity = US real GDP; Australia
  trades mostly with Asia. This is documented and deliberate: as of
  2026-07-04 no fresh machine-readable trade-weighted or China activity
  series exists across the wired providers (OECD/G20 and FRED China GDP both
  frozen at 2023Q3) — and adding a stale series would truncate the entire
  balanced panel to its end-date. Commodity prices carry part of the China
  signal. *Scoped extensions:* a manually-supplied trading-partner GDP file,
  or ragged-edge estimation (README D22).
- **Combination gains are modest by design** — that is the combination
  puzzle, and the pool's payoff is insurance and calibration, not headline
  accuracy. Where a single member beats the pools, the tables say so.
- **The SV engine cannot do exact conditional scenarios** (its shocks are
  non-Gaussian); scenario forecasts pool the Gaussian-engine members and are
  labelled as such.
- **Quarterly cadence only.** Monthly indicators (labour force, the monthly
  CPI indicator) are not exploited for nowcasting; a mixed-frequency layer
  feeding the h = 1 jump-off is the natural next extension after vintages.
